\chapter*{Appendices}
\addcontentsline{toc}{chapter}{Appendices}

\section*{Appendix A: Supabase Database Schema}

The complete PostgreSQL DDL script (\texttt{supabase/schema.sql}) defines 14 interconnected tables with PostGIS spatial extensions, enumerated types for vehicle and reservation statuses, and trigger functions for automated timestamp updates. Key tables include:

\begin{itemize}
    \item \texttt{profiles}: User identity and license verification.
    \item \texttt{vehicles}: Fleet inventory with real-time location (PostGIS geography).
    \item \texttt{reservations}: Holds vehicles for riders before QR scan.
    \item \texttt{rides}: Active trips with telemetry and fare calculation.
    \item \texttt{payments}: Transaction records linked to completed rides.
    \item \texttt{vehicle\_locations}: Historical GPS waypoints for analytics.
\end{itemize}

Refer to the attached \texttt{schema.sql} file in the digital submission for full implementation details.

\section*{Appendix B: Seed Data Script}

The \texttt{supabase/seed.sql} file populates initial test data:

\begin{itemize}
    \item A standard pricing rule (base fee 9.90 TRY, unlock fee 4.50 TRY, per-minute 3.20 TRY, per-km 2.00 TRY).
    \item Five quadricycles (RQ-001 through RQ-005) positioned at geographic coordinates in Gebze with battery percentages ranging from 58\% to 91\%.
\end{itemize}

This seed data enables immediate testing of reservation and ride workflows without manual database entry.

\section*{Appendix C: Mobile Application Source Code Structure}

The React Native workspace comprises approximately 3,000 lines of code organized as follows:

\begin{itemize}
    \item \texttt{App.js}: Root navigator with authentication gating.
    \item \texttt{screens/}: Five tab screens (Home, Explore, ScanQR, Profile, Settings) plus Auth and Details.
    \item \texttt{components/RideDetailsCard.js}: Reusable card component for active rental display.
    \item \texttt{context/AuthContext.js}: Global session management with Supabase Auth.
    \item \texttt{hooks/useRentalFlow.js}: Rental state machine with ten phases.
    \item \texttt{lib/supabaseClient.js}: Singleton Supabase client initialization.
    \item \texttt{lib/vehicleUtils.js}: Utility for formatting vehicle titles.
\end{itemize}

Complete source code is available in the accompanying digital archive submitted with this thesis and at \url{https://github.com/emreglc/rentquad}.